---
title: "HW 6"
author: "Jacob Haussler, Brad, Syed, Katie"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
#housePriceCat <- read.csv("./housePriceCat.csv")
housePriceCat <- read.csv("C:/Users/Brad/Desktop/Stat 4020/housePriceCat.csv")
dat <- housePriceCat
```


#### 1. Fit a MLR model by regressing price on sqft and view. Write the equation of the fitted line.

```{r}
mlr.dummy <- lm(price ~ sqft + factor(view), data= dat)
summary(mlr.dummy)
```

Regression Line: price_hat = 135088.1 + 534.9(sqft) - 719122.4(view(mountain)) - 845262.3(view(wood))

#### 2. Test if view has a significant impact on house price.

```{r}
library(car)

linearHypothesis(mlr.dummy, c("factor(view)mountain = factor(view)wood", "factor(view)mountain = 0"))
```

- Based off the p-value we would reject the null hypothesis. This shows that the response variable is significantly impacted by the categorical variable. 

#### 3. Test if house price differs significantly between mountain view and wood view keeping sqft constant.
```{r}
linearHypothesis(mlr.dummy, c("factor(view)mountain = factor(view)wood"))
```

- Based on the p-value we would fail to reject the null hypothesis. This means that we cannot determine that view = mountain and view = wood have different intercepts. 

#### 4. Investigate the presence of interaction effect.
```{r}
mlr.interaction <- lm(price ~ sqft * factor(view), data = dat)
summary(mlr.interaction)
```

- Here we can see that none of the interaction effects are significant. This means that there is not evidence of the response being significantly impacted by the view regressor variable.

# Q2. [5 points] Consider housePriceCat.csv

# 1. Fit a MLR model by regressing price on waterfront only. Write the equation of the fitted line.
```{r}
mlr <- lm(price ~ waterfront, data = dat)
summary(mlr)
```

Regression line: hat(price) = 998308 + 572672*Waterfront

# 2. Write the fitted regression line for waterfront = 0.

hat(price) = 998308 + 572672*(0)
=
hat(price) = 998308

# 3. Write the fitted regression line for waterfront = 1.

hat(price) = 998308+572672 *(1)
hat(price) = 1570980

# 4. Compute a 95% confidence interval for the mean house price with no waterfront.
```{r}
confint(mlr, level = 0.95)
```

Confidence Interval with no waterfront:
Lower: 650611.7 
Upper: 1346005

# 5. Compute a 95% confidence interval for the difference in mean house price for waterfront vs. no waterfront.

Confidence Interval with waterfront:
Lower: 650611.7 - 264692.8 = 385918.9
Upper: 1346005 + 1410036 = 2756041

Difference between with and without waterfront:
Lower: abs(650611.7 - 385918.9) = 264692.8
Upper: abs(1346005 - 2756041) = 1410036
