---
title: "HW 6"
author: "Jacob Haussler"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
housePriceCat <- read.csv("./housePriceCat.csv")
dat <- housePriceCat
```


#### 1. Fit a MLR model by regressing price on sqft and view. Write the equation of the fitted line.
```{r}
dat$new_view = 0
dat$new_view[dat$view == "wood"] <-0
dat$new_view[dat$view == "city"] <-1
dat$new_view[dat$view == "mountain"] <-2
```
```{r}
dat$dummy1 <- ifelse(dat$new_view == 1, 1,0)
dat$dummy2 <- ifelse(dat$new_view == 2, 1,0)
head(dat)
```
```{r}
mlr.dummy <- lm(price ~ sqft + factor(view), data= dat)
summary(mlr.dummy)
# fitted value -  hat(price) = -710174 + 534.9 * sqft +845262.3 * View(city) + 126139.9 * View(mountain)
# when view = wood ; hat(price) = -710174 + 534.9 * sqft
# when view = city ; hat(price) = (-710174+845262.3) + 534.9 * sqft
# when view = mountain ; hat(price) = (-710174+126139.9) + 534.9 * sqft
```

#### 2. Test if view has a significant impact on house price.
```{r}
mlr2 <- lm(price ~ sqft + factor(view), data = dat)
summary(mlr2)
```

```{r}
library(car)

linearHypothesis(mlr2, c("factor(view)mountain = factor(view)wood", "factor(view)mountain = 0"))
```

- Based off the p-value we would reject the null hypothisis. This shows that the response variable is significantly impacted by the categorical variable. 

#### 3. Test if house price differs significantly between mountain view and wood view keeping sqft constant.
```{r}
linearHypothesis(mlr2, c("factor(view)mountain = factor(view)wood"))
```

- Based on the p-value we would fail to reject the null hypothesis. This means that we cannot determine that view = mountain and view = wood have diffrent intercepts. 

#### 4. Investigate the presence of interaction effect.
```{r}
mlr.interaction <- lm(price ~ sqft * factor(view), data = dat)
summary(mlr.interaction)
```

- Here we can see that none of the interaction effects are significant.


# Q2. [5 points] Consider housePriceCat.csv

# Fit a MLR model by regressing price on waterfront only. Write the equation of the fitted line.
```{r}
housePriceCat <- read.csv("./housePriceCat.csv")
dat <- housePriceCat
mlr <- lm(price ~ waterfront, data = dat)
summary(mlr)
#hat(price) = 998308 + 572672*Waterfront
```


# Write the fitted regression line for waterfront = 0.
```{r}
#hat(price) = 998308
```


# Write the fitted regression line for waterfront = 1.
```{r}
# hat(price) = 998308+572672
# hat(price) = 1570980
```

# Compute a 95% confidence interval for the mean house price with no waterfront.
```{r}
confint(mlr, level = 0.95)
# Lower - 650611.7 
# Upper - 1346005
```

# Compute a 95% confidence interval for the difference in mean house price for waterfront vs. no waterfront.
```{r}
# how to do this
```

